%-------------------------
% Customized Resume in LaTeX
% Author : Samir Sharma
%-------------------------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
% Removed the conflicting fullpage package
%\usepackage[empty]{fullpage}
% Added T1 font encoding before loading fonts
\usepackage[T1]{fontenc}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{setspace}
\usepackage{amsfonts}
\usepackage{tabularx}

\usepackage[top=0.6in, bottom=0.6in, left=0.7in, right=0.7in]{geometry}

\urlstyle{same}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}

\definecolor{headings}{RGB}{41, 128, 185}
\definecolor{accent}{RGB}{44, 62, 80}
\definecolor{bullet}{RGB}{41, 128, 185}

\usepackage[defaultsans]{lato}
\renewcommand{\familydefault}{\sfdefault}

\titleformat{\section}{
  \color{headings}\scshape\Large\bfseries
}{\thesection}{1em}{}
\titlespacing*{\section}{0pt}{1.5ex plus 1ex minus .2ex}{1ex plus .2ex}

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1\vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    {\textbf{#1} \hfill #2}\\
    {\textit{#3} \hfill \textit{#4}}\vspace{-8pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    {\textbf{#1} \hfill #2}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{\faCircle}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Samir Sharma} \\ \vspace{1pt}
    \footnotesize
    \makebox[\textwidth][c]{%
    \href{mailto:resume@samirsharma.ca}{\color{accent}\faEnvelope\ \ resume@samirsharma.ca} \ $|$ \
    \href{https://www.linkedin.com/in/samir-rsharma/}{\color{accent}\faLinkedin\ \ linkedin.com/in/samir-rsharma} \ $|$ \
    \href{https://github.com/SamirRSharma}{\color{accent}\faGithub\ \ github.com/SamirRSharma} \ $|$ \
    \href{https://www.samirsharma.ca}{\color{accent}\faGlobe\ \ www.samirsharma.ca}%
    }
\end{center}

%-----------TECHNICAL SKILLS-----------
\section*{\color{headings}Technical Skills}
 \resumeSubHeadingListStart
    \small{
      \item{
        \textbf{Languages}{: HTML/CSS, Python, C++, JavaScript, TypeScript, SQL, Java, \LaTeX} \\
        \textbf{Frameworks/Libraries}{: React, Node.js, Flask, PyTorch, OpenCV, YOLO, Docker} \\
        \textbf{Databases/Tools}{: MongoDB, MySQL, SQLite, Docker, Git, Bash}
        }
    }
 \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section*{\color{headings}Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineering Intern}{June 2024 -- Sep. 2024}
      {Quickly}{Calgary, AB, Canada}
      \resumeItemListStart
        \resumeItem{Optimized platform features by \textbf{refactoring backend code} in \textbf{Node.js}, reducing average loading times by \textbf{23\%} and enhancing user experience.}
        \resumeItem{Resolved \textbf{15 critical bugs} over 4 weeks by collaborating with a team of 4 software engineers, significantly improving system stability.}
        \resumeItem{Developed validation systems using \textbf{Yup} and \textbf{TypeScript}, cutting database errors by \textbf{30\%}, and authored API documentation, decreasing customer inquiries by \textbf{70\%}.}
        \resumeItem{Conducted code reviews to ensure code quality and adherence to best practices in \textbf{Git} workflows.}
      \resumeItemListEnd

    \resumeSubheading
      {Minecraft Server Programmer}{Sep. 2021 -- June 2023}
      {Independent Project}{Calgary, AB, Canada}
      \resumeItemListStart
        \resumeItem{Built a high-performance \textbf{Minecraft server} using \textbf{Java} and \textbf{Spigot API}, supporting \textbf{5,000 concurrent users} and over \textbf{30,000 unique players}.}
        \resumeItem{Created custom \textbf{gameplay plugins in Java} to enhance gameplay and ensure robust server management.}
        \resumeItem{Boosted player engagement by integrating external \textbf{APIs} to automate reward systems.}
        \resumeItem{Raised \textbf{\$6,000} for Ukrainian aid by developing and managing a \textbf{donation platform} and in-game store.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section*{\color{headings}Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Fullstack Bionic Hand} $|$ \emph{JavaScript, Tailwind, MongoDB, Node.js, AWS EC2, API}}{Hack the North 2024}
      \resumeItemListStart
        \resumeItem{Tied for \textbf{finalist}, top 12 out of 239 teams at Hack the North 2024, Canada's largest hackathon.}
        \resumeItem{Developed a \textbf{bionic hand} controlled by \textbf{EMG and ECG signals}, utilizing a \textbf{language model} for signal interpretation.}
        \resumeItem{Linked the device to a \textbf{full-stack application} via \textbf{WebSockets} to display live stats and enable key binding functionality.}
        \resumeItem{Secured over \textbf{\$9,000} in prizes.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{ML Tennis Analysis System} $|$ \emph{Python, YOLO, PyTorch, OpenCV}}{June 2023 -- Nov. 2023}
      \resumeItemListStart
        \resumeItem{Developed an \textbf{object detection system} using \textbf{YOLO} to detect and track players and tennis balls in video footage.}
        \resumeItem{Implemented a model to identify court key points, enabling accurate \textbf{player positioning} and automated \textbf{in/out calls}.}
        \resumeItem{Enhanced detection accuracy for fast-moving tennis balls by training custom \textbf{CNNs}.}
        \resumeItem{Utilized \textbf{PyTorch} for model training and \textbf{OpenCV} for video processing and visualization.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Full Stack AI Object Detection App} $|$ \emph{Hugging Face, Docker, AWS, Next.js}}{Feb. 2024 -- May 2024}
      \resumeItemListStart
        \resumeItem{Built a \textbf{web app} allowing users to perform \textbf{object detection} on images using \textbf{Hugging Face} models.}
        \resumeItem{Containerized the application with \textbf{Docker} and deployed it on \textbf{AWS EC2} for scalable cloud hosting.}
        \resumeItem{Implemented image upload functionality on a \textbf{full-stack} application.}
        \resumeItem{Enhanced user experience by utilizing \textbf{Next.js} for front-end development.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section*{\color{headings}Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{Sep. 2024}
      {Bachelor of Mathematics, Honours Co-op Program}{Waterloo, ON, Canada}
      \resumeItemListStart
        \resumeItem{\textbf{Activities}: Math Society Speaker, Residence Council South President, Data Science Club, Computer Science Club}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
